module2IVgraphs

### 2022-04-10 combined data set/demographicvariables.Rmd
add colour to state wise graph

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"
module2 %>%
  filter(!row_number() %in% c(1,2))

@@

codedmodule2

@@

moduleone <- read_excel(here::here("thesis_surveydata/livelihood_insecurity_complete.xlsx"))
save(moduleone, file = "moduleone.rda")
module1 <- data.frame(moduleone)
module1 %>%
  filter(!row_number() %in% c(1,2))

@@

  mutate_at(vars(Livelihood_Income), funs(case_when(. == "(a) own farming/fishing/animal rearing/business" ~ "LSI", 
                                                    . == "(b) employed for wages/salary" ~ "ISI",
                                                    . == "(c) student" ~"student",
                                                    . == "(d) currently unemployed" ~ "unemployed",
                                                    . == "(e) homemaker" ~ "homemaker",
                                                    . == "(f) retired" ~ "retired",
                                                    . == "(g) unable to work" ~ "unable to work" ))) %>%

# coding education
   mutate_at(vars(education), funs(case_when(. == "No schooling completed" ~ 0, 
                                                                        . == "Primary school" ~ 1,
                                                                        . == "Grade 10th" ~ 2,
                                                                        . == "Grade 12th" ~ 3,
                                                                        . == "Some college, no degree" ~ 4,
                                                                        . == "Trade/technical/vocational training" ~ 5,
                                                                        . == "Bachelor's degree" ~ 6,
                                                                        . == "Master's degree" ~ 7,
                                                                        . == "Professional degree" ~ 8,
                                                                        . == "Doctorate degree" ~ 9 ))) %>%
# coding yes and no questions
  mutate_at(vars(Iassociation, govtscheme, wateravail, polposition, polparty), funs(case_when(.== "Yes" ~ 1,
                                            .== "No" ~ 0))) %>%
# reverse coding yes and no questions
  mutate_at(vars(illness,severeillness), funs(case_when(.== "Yes" ~ 0,
                                            .== "No" ~ 1))) %>%

# coding How confident are you that you can continue your current livelihood if you want to? 
 mutate_at(vars(Lconfidence), funs(case_when(. == "Not at all confident" ~ 1, 
                                                                        . == "Not much confident" ~ 2,
                                                                        . == "Neutral" ~3,
                                                                        . == "Somewhat confident" ~ 4,
                                                                        . == "Very confident" ~ 5))) %>%

 mutate_at(vars(Lboat, houseown), funs(case_when(.== "Own it" ~ 1,
                                                 .== "Rent it" ~ 0)))%>%

# J security index coding

 mutate_at(vars(JISRkeep), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5))) %>%

# reverse code JIS 
  mutate_at(vars(JISlosefuture, JISlose, JISfuture), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                        . == "Somewhat disagree" ~ 4,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 2,
                                                                        . == "Strongly agree" ~ 1))) %>%

  mutate_at(vars(totalincome, otherincome), funs(case_when(. == "Less than Rs 1,00,000" ~ 1,
                                                                        . == "Rs 1,00,000 to Rs 2,50,000"  ~ 2,
                                                                        . == "Rs 2,50,001 to Rs 5,00,000" ~ 3,
                                                                        . == "Rs 5,00,001 to Rs 10,00,000" ~ 4,
                                                                        . == "Rs 10,00,001 and above"  ~ 5))) %>%

  mutate_at(vars(workknowledge, subsidyknow), funs(case_when(. == "Very poor" ~ 1, 
                                                                        . == "Poor" ~ 2,
                                                                        . == "Fair" ~3,
                                                                        . == "Good" ~ 4,
                                                                        . == "Very good" ~ 5))) %>%

mutate_at(vars(drinkingwater, cookingwater), funs(case_when(. == "Bottled water/ Filtered Water" ~ 1,                                       
                                                          .  == "Piped into dwelling" ~ 2,                                                  
                                                          .  == "Piped to neighbour" ~ 3,                                                   
                                                          .  == "Piped to yard/plot" ~ 4, 
                                                          .  == "Protected well" ~ 5, 
                                                          .  == "Public tap/standpipe" ~6,
                                                          .  == "Surface Water  (River/Dam/Lake/Pond/Stream/Canal/Irrigation Channel)" ~7, 
                                                          .  == "Tanker Truck" ~ 8,
                                                          .  == "Tubewell/borehole" ~ 9,
                                                          .  == "Unprotected Spring" ~ 10))) %>%

  mutate_at(vars(toilet), funs(case_when(. == "No facility/bush/field" ~ 1,                                       
                                                          .  == "Hanging toilet/hanging latrine" ~ 2,                                             
                                                          .  == "Bucket toilet"  ~ 3,                                                   
                                                          .  == "Composting toilet"  ~ 4, 
                                                          .  == "Pit latrine without slab/open pit" ~ 5, 
                                                          .  == "Pit latrine with slab" ~6,
                                                          .  == "Ventilated improved pit laterine"  ~7, 
                                                          .  == "Flush to somewhere else"  ~ 8,
                                                          .  == "Flush to pit latrine"  ~ 9,
                                                          .  == "Flush to septic tank" ~ 10,
                                                          .  == "Flush to piped sewer system" ~ 11))) %>%

  mutate_at(vars(house), funs(case_when(. == "Hut made of mud, bamboo, straw etc. (kutcha house)" ~ 1, 
                                        . == "Permanent single story house (pukka house)" ~ 2,
                                        . == "Apartment/Flat in a multi-story building"  ~3,
                                        . == "Multi-story house" ~ 4))) %>%

  mutate_at(vars(foodtrouble), funs(case_when(. == "8 or more months" ~ 1,                                       
                                                          .  == "6-8 months"  ~ 2,                                                  
                                                          .  == "4-6 months"  ~ 3,                                                   
                                                          .  == "2-4 months"  ~ 4, 
                                                          .  == "1-2 months" ~ 5, 
                                                          .  == "0 months"  ~6))) %>%

   mutate_at(vars(foodadequacy), funs(case_when(. == "Extremely inadequate" ~ 1, 
                                                                        . == "Moderately inadequate" ~ 2,
                                                                        . == "Slightly inadequate" ~3,
                                                                        . == "Neither adequate nor inadequate" ~ 4,
                                                                        . == "Slightly adequate" ~ 5,
                                                                        . == "Moderately adequate" ~ 6,
                                                                        . == "Extremely adequate" ~ 7)))%>%

separate( col = cookstove, into = c("cook1", "cook2", "cook3", "cook4"), sep = ",") %>%
separate( col = vehicle, into = c("vehicle1", "vehicle2", "vehicle3", "vehicle4"), sep = ",")%>%
separate( col = foodsource, into = c("food1", "food2", "food3", "food4"), sep = ",")

#coded dependent variables for module 1 livelihood and income security survey

codedmodule1 
```

@@

joineddf
```

@@

@@

castegendereffect %>%
  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_Brahmin", "Female_SC", "Female_OBC", "Male_SC","Male_ST", "Male_General", "Female_General","Female_ST" ,"Male_OBC", "Male_Brahmin")))%>%
  select(!starts_with(c("Risky_IND")))%>%
  #select("Risky_Hydro", "Risky_Nuclear", "Risky_Coal","Gender_Caste")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(riskscore = mean(c_across(Risky_Hydro:Risky_Oil))) %>%
  select(Gender_Caste, riskscore) %>%
  dplyr::group_by(Gender_Caste)%>%
  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(y = Gender_Caste, x = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
                 position=position_dodge(.9))
#%>%

@@

@@

 # mean risk from indicidually or community owned energy technologies

castegendereffect %>%
  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_OBC","Female_SC", "Female_ST" ,"Female_Brahmin", "Male_ST",  "Male_SC","Female_General", "Male_General", "Male_OBC", "Male_Brahmin")))%>%
  select(starts_with(c("Risky_IND", "Gender_Caste")))%>%
  #select("Risky_Hydro", "Risky_Nuclear", "Risky_Coal","Gender_Caste")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(riskscore = mean(c_across(Risky_INDHydro:Risky_INDLPG))) %>%
  select(Gender_Caste, riskscore) %>%
  dplyr::group_by(Gender_Caste)%>%
  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(y = Gender_Caste, x = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
                 position=position_dodge(.9))

@@

@@

castegendereffect %>%
  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_Brahmin","Male_General", "Male_OBC", "Female_SC","Male_ST", "Male_SC","Female_ST", "Female_General", "Female_OBC","Male_Brahmin")))%>%
  select(!starts_with(c("Risky_IND")))%>%
  select("Risky_Hydro", "Risky_Nuclear", "Risky_Coal","Gender_Caste")%>%
  na.omit()%>%
  dplyr::group_by(Gender_Caste)%>%
  summarise(hydro_m=mean(Risky_Hydro), hydro_sd=sd(Risky_Hydro), nuclear_m=mean(Risky_Nuclear), nuclear_sd=sd(Risky_Nuclear),            coal_m=mean(Risky_Coal),   coal_sd=sd(Risky_Coal))%>%
  arrange(desc(hydro_m))%>%
  ggplot(aes(y = Gender_Caste, x = hydro_m))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(xmin=hydro_m-hydro_sd, xmax=hydro_m + hydro_sd), width=.2,
                 position=position_dodge(.9))
```

# centrally managed by urban and rural

@@

joineddf %>%
  select(starts_with(c("Risky", "urban_rural")))%>%
  select(!starts_with(c("Risky_IND")))%>%
  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(riskscore = mean(c_across(Risky_Hydro:Risky_Oil))) %>%
  select(urban_rural, riskscore) %>%
  dplyr::group_by(urban_rural)%>%
  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= urban_rural, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))
```

@@

joineddf %>%
  select(starts_with(c("Risky", "gender")))%>%
  select(!starts_with(c("Risky_IND")))%>%
  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(riskscore = mean(c_across(Risky_Hydro:Risky_Oil))) %>%
  select(gender, riskscore) %>%
  dplyr::group_by(gender)%>%
  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= gender, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))
```

@@

joineddf %>%
  select(starts_with(c("Risky", "gender")))%>%
  select(starts_with(c("Risky_IND", "gender")))%>%
  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(riskscore = mean(c_across(Risky_INDHydro:Risky_INDLPG))) %>%
  select(gender, riskscore) %>%
  dplyr::group_by(gender)%>%
  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= gender, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))
```

@@

@@

@@

@@

@@

cenrisksummary %>%
  mutate(technology = fct_reorder(technology, mean, .desc = TRUE))%>%
  ggplot(aes(x= technology, y= mean))+
  geom_bar(stat="identity", position=position_dodge())+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  ylim(0,5)+
  facet_wrap(~ State)+
  #scale_fill_manual(y, values =))+
  coord_flip()

>>>>

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
module2 <- data.frame(moduletwo)
module2[module2 == "Rather not say/ Don't know"] <- "Rather not say/Don't know"

@@

@@

moduleone <- read_excel(here::here("thesis_surveydata/livelihood_insecurity_complete.xlsx"))
module1 <- data.frame(moduleone)

@@

# replace nuclear acceptance likert scale with numbers
  mutate_at(vars(N_accept,N_reluctantlyaccept,N_reject), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                        . == "Somewhat disagree" ~ 2,
                                                                        . == "Neither agree nor disagree" ~3,
                                                                        . == "Somewhat agree" ~ 4,
                                                                        . == "Strongly agree" ~ 5)))

@@

@@

##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender and caste groups

OBC = Other Backward Classes
SC = Scheduled Castes
ST = Scheduled Tribes

@@

castegendereffect %>%
  mutate(Gender_Caste = factor(castegendereffect$Gender_Caste, levels = c("Female_Brahmin", "Female_SC", "Female_OBC", "Male_SC","Male_ST", "Male_General", "Female_General","Female_ST" ,"Male_OBC", "Male_Brahmin")))%>%
  select(!starts_with(c("Risky_IND")))%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(riskscore = mean(c_across(Risky_Hydro:Risky_Oil))) %>%
  select(Gender_Caste, riskscore) %>%
  dplyr::group_by(Gender_Caste)%>%
  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(y = Gender_Caste, x = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(x = "mean perceived risk", y = "GenderXCaste groups")

@@

##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender and caste groups

OBC = Other Backward Classes
SC = Scheduled Castes
ST = Scheduled Tribes

@@

# mean risk from individually or community owned energy technologies

castegendereffect %>%
  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_OBC","Female_SC", "Female_ST" ,"Female_Brahmin", "Male_ST",  "Male_SC","Female_General", "Male_General", "Male_OBC", "Male_Brahmin")))%>%
  select(starts_with(c("Risky_IND", "Gender_Caste")))%>%
  #select("Risky_Hydro", "Risky_Nuclear", "Risky_Coal","Gender_Caste")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(riskscore = mean(c_across(Risky_INDHydro:Risky_INDLPG))) %>%
  select(Gender_Caste, riskscore) %>%
  dplyr::group_by(Gender_Caste)%>%
  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(y = Gender_Caste, x = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(x = "mean perceived risk", y = "GenderXCaste groups")

@@

##Perceived Risk Scores for centrally managed hydroelectric dams by gender and caste groups

OBC = Other Backward Classes
SC = Scheduled Castes
ST = Scheduled Tribes

@@

castegendereffect %>%
  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_Brahmin","Male_ST","Male_Brahmin", "Male_SC","Female_General","Male_General", "Female_OBC", "Female_ST","Female_SC", "Male_OBC")))%>%
  select(!starts_with(c("Risky_IND")))%>%
  select("Risky_Hydro", "Risky_Nuclear", "Risky_Coal","Gender_Caste")%>%
  na.omit()%>%
  dplyr::group_by(Gender_Caste)%>%
  summarise(hydro_m=mean(Risky_Hydro), hydro_sd=sd(Risky_Hydro), nuclear_m=mean(Risky_Nuclear), nuclear_sd=sd(Risky_Nuclear),            coal_m=mean(Risky_Coal),   coal_sd=sd(Risky_Coal))%>%
  arrange(desc(hydro_m))%>%
  ggplot(aes(y = Gender_Caste, x = hydro_m))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(xmin=hydro_m-hydro_sd, xmax=hydro_m + hydro_sd), width=.2,
                 position=position_dodge(.9))+
  labs(x = "mean perceived risk", y = "GenderXCaste groups")
```

##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by urban or rural location of the respondent

@@

joineddf %>%
  select(starts_with(c("Risky", "urban_rural")))%>%
  select(!starts_with(c("Risky_IND")))%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(riskscore = mean(c_across(Risky_Hydro:Risky_Oil))) %>%
  select(urban_rural, riskscore) %>%
  dplyr::group_by(urban_rural)%>%
  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= urban_rural, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(x = "urban or rural", y = "mean risk")
```

##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender

@@

joineddf %>%
  select(starts_with(c("Risky", "gender")))%>%
  select(!starts_with(c("Risky_IND")))%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(riskscore = mean(c_across(Risky_Hydro:Risky_Oil))) %>%
  select(gender, riskscore) %>%
  dplyr::group_by(gender)%>%
  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= gender, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(y = "mean risk")
```

##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender.

@@

joineddf %>%
  select(starts_with(c("Risky", "gender")))%>%
  select(starts_with(c("Risky_IND", "gender")))%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(riskscore = mean(c_across(Risky_INDHydro:Risky_INDLPG))) %>%
  select(gender, riskscore) %>%
  dplyr::group_by(gender)%>%
  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= gender, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(y = "mean risk")
```

##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by religion

@@

##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by religion.

@@

##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by age

@@

##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by age.

@@

##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by state

@@

cenrisksummary %>%
  mutate(technology = fct_reorder(technology, mean, .desc = TRUE))%>%
  ggplot(aes(y= technology, x= mean, fill = technology))+
  geom_bar(stat="identity", position=position_dodge())+
  theme_minimal()+
  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  scale_fill_manual(values=c("#74238B", "#FEF102","#484349","#BA5C12", "#4D9DE0","#CFEBDF", "#FA6728"))+
  xlim(0,5)+
  facet_wrap(~ State)
  #scale_fill_manual(y, values =))+

### 2022-04-10 module2/module2IVgraphs.Rmd
add colour to state wise graph

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(hablar))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(ggbiplot))
suppressPackageStartupMessages(library(psych)) # psychometrics

>>>>

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(ggplot2))
